|

### 2016-05-15 _archieve_/itraquant/MANUAL/iTRAQ4_Quantification.Rmd
reorganize

```{r}
# Prior Filtering
length(msexp.id)
k                 <- (fData(msexp.id)$'ms-gf:evalue'< evalue_treshold)
k[is.na(k)]       <- FALSE
msexp.filter1     <- removeNoId(msexp.id, keep=k)
length(msexp.filter1)
msexp.filter2     <- removeMultipleAssignment(msexp.filter1)
length(msexp.filter2)
fData(msexp.filter2)[1:3,]
```

##Quantification
Quantification is done by using the MSnBase package [@msnbase], with method specified on the `p3.config` file.
```{r}
head(exprs(qnt))
qnt.filtered      <- filterNA(qnt, pNA = pNA)
head(exprs(qnt.filtered))
```

##Results
subsequently, the features are aggregated by accession ID, with the value calculated using the function denoted on the `p3.config`.
```{r}
length(exprs(qnt))
result  <- combineFeatures(qnt, groupBy = fData(qnt)$accession, fun=combine_by)
length(exprs(result))
head(exprs(result))
```

>>>>

```{r}
# Prior Filtering
length(msexp.id)
print(evalue_treshold)
k                 <- (fData(msexp.id)$'ms-gf:evalue'< evalue_treshold)
k[is.na(k)]       <- FALSE
print(sum(k)) # Number of kept features
msexp.filter1     <- removeNoId(msexp.id, keep=k)
# Subsquent evalue filter
length(msexp.filter1)
msexp.filter2     <- removeMultipleAssignment(msexp.filter1)
# Subsquent multiple assigment filter
length(msexp.filter2)
fData(msexp.filter2)[1:3,]
```

##Quantification
Quantification is done by using the MSnBase package [@msnbase], with method specified on the `p3.config` file.
```{r}
head(exprs(qnt))
print(pNA)
qnt.filtered      <- filterNA(qnt, pNA = pNA)
head(exprs(qnt.filtered))
```

##Results
subsequently, the features are aggregated by accession ID, with the value calculated using the function denoted on the `p3.config`.
```{r}
length(exprs(qnt.filtered))
result  <- combineFeatures(qnt.filtered, groupBy = fData(qnt.filtered)$accession, fun=combine_by)
length(exprs(result))
head(exprs(result))
```

### 2016-05-15 _archieve_/scquant/MANUAL/SpectrumCount_Quantification.Rmd
reorganize

---
title: | 
  | Portable Proteomics Pipeline (P3) 
  | Spectrum Count Quantification
author: "Daniel Kristiyanto (daniel.kristiyanto@pnnl.gov)"
date: \today
fontsize: 11pt
output: pdf_document
bibliography: ref.bib
csl: biomed-central.csl
header-includes:
  \usepackage{fancyhdr}
  \usepackage{graphicx}
  \usepackage{hyperref}
  \pagestyle{fancy}
  \setlength\headheight{28pt}
  \rhead{\includegraphics[width = .2\textwidth]{pnnllogo.png}}
  \fancyfoot[LE,RO]{kristiyanto/p3:scquant}
---
\rule{\textwidth}{1pt}
Portable Proteomics Pipeline (P3) is a series of protein mass spectrometry data pre-processing pipelines in Docker containers. The packages includes protein identification, filtering, and quantification for both labeled and label-free mass spectrometry data.

This document discuss the ```kristiyanto/p3:scquant``` container, a spectrum count quantification pipeline for label-free mass spectrometry protein quantification. The pipeline is based on MSnID pipeline [@msnid].

@@

## Filter
Filtering is done by using the parameter defined in the ```p3.config``` file. The filtering is including the error calculation (`variable: error_treshold`), scoring (`variable: score_treshold`), and filter optimization (`variable: iteration and fdr`).
```{r}
show(mzid)
show(fObj)
evaluate_filter(prj, fObj, level="PSM")
evaluate_filter(prj, fObj, level="peptide")
evaluate_filter(prj, fObj, level="accession")
show(prj)
```
##Quantification
Quantification is done by using the MSnBase package [@msnbase].
```{r}
msnset  <- as(prj, "MSnSet")
msnset  <- combineFeatures(msnset, fData(msnset)$accession, redundancy.handler="unique", 
                           fun="sum",cv=FALSE)
```

>>>>

---
title: | 
  | Portable Proteomics Pipeline (P3) 
  | Spectrum Count Quantification
author: "Daniel Kristiyanto (daniel.kristiyanto@pnnl.gov)"
date: \today
fontsize: 11pt
output: pdf_document
bibliography: ../../media/ref.bib
csl: ../../media/biomed-central.csl
header-includes:
  \usepackage{fancyhdr}
  \usepackage{graphicx}
  \usepackage{hyperref}
  \pagestyle{fancy}
  \setlength\headheight{28pt}
  \rhead{\includegraphics[width = .2\textwidth]{../../media/pnnllogo.png}}
  \fancyfoot[LE,RO]{kristiyanto/p3:scquant}
---
\rule{\textwidth}{1pt}
Portable Proteomics Pipeline (P3) is a series of protein mass spectrometry data pre-processing pipelines in Docker containers. The packages includes protein identification, filtering, and quantification for both labeled and label-free mass spectrometry data.

This document discuss the ```kristiyanto/p3:scquant``` container, a spectrum count quantification pipeline for label-free mass spectrometry protein quantification. The pipeline is based on MSnID pipeline [@msnid, @MSnID31].

@@

## Filter
Filtering is done by using the parameter defined in the ```p3.config``` file. The filtering is including the error calculation (`variable: error_treshold`), scoring (`variable: score_treshold`), and filter optimization (`variable: iteration and fdr`) [@deutsch2010mass, @MSnID31].
```{r}
show(mzid)
show(fObj)
evaluate_filter(prj, fObj, level="PSM")
evaluate_filter(prj, fObj, level="peptide")
evaluate_filter(prj, fObj, level="accession")
show(prj)
```
##Quantification
Quantification is done by using the MSnBase package [@msnbase].
```{r}
msnset  <- as(prj, "MSnSet")
msnset  <- combineFeatures(msnset, fData(msnset)$accession, redundancy.handler="unique", 
                           fun="sum",cv=FALSE)
```
